\subsection{What is the Design Process?}
The development of a modern system or product is complex and requires a lot of planning. A design process lays the foundation for such planning by categorizing the development into the five most essential stages: \cite{Understanding_the_design_process}

\begin{itemize}
  \item \textbf{Emphasize}: This stage involves getting data about the user base and target audience. To successfully build a system or product, one needs to know who and how they will interact with the project. 
  \item \textbf{Define}: The next step is to define the problem that needs to be solved by narrowing down the data to get the most common problems. 
  \item \textbf{Ideate}: Once the problems are defined, thinking about possible solutions and gathering ideas is the next stage in development. 
  \item \textbf{Prototype}: Next is designing a mock-up prototype to visualize the idea.
  \item \textbf{Test}: The final stage is testing with test users to validate your ideas.  
\end{itemize}

\subsection{Requirement and Software Engineering }
The stages of the design process can be separated into two aspects of software development: software engineering and requirement engineering.  
Software engineering specializes in developing the technical part of the process. It decides, for example, what framework to use, which software patterns are most suitable, and how to best test the code. But software engineering alone lacks the data to make those decisions. \cite{What_Does_a_Software_Developer_Do}
Requirements engineering develops the scope of the project by understanding the target audiences’ needs, motivations, and goals. Requirements engineering can be categorized into four key tasks: \cite{Requirements_Engineering_Process_in_Software_Engineering} 

\begin{itemize}
  \item \textbf{Feasibility study}: The feasibility study analyzes, for example, if the project is technically feasible and economically profitable and if the developers have enough resources like time and staff to develop the project. 
  \item \textbf{Requirements elicitation}: The elicitation step focuses on getting to know the stakeholders, a group of people that have an interest or share in the project \cite{Stakeholders_in_Requirements_Engineering}, and figuring out the needs and expectations of the end-user. But elicitation also includes gathering data about technical requirements, for example, standards in the industry and similar projects.
  \item \textbf{Requirements specification}: Requirement specification develops functional and formal requirement models from the data gathered in the previous step. Such models include functional requirements: what can the system do, and non-functional requirements: how well should the system be able to do them. 
  \item \textbf{Requirements validation}: The final task is to validate the requirements. A valid requirement would, for example, be consistent and not conflict with any other requirement, or it needs to be practically achievable. 
\end{itemize}

\subsection{The Role of Personas and Demographics in Requirement Engineering}
Requirement engineering needs a lot of data to develop the scope of the project and specify the requirements. Especially the requirements elicitation and analysis stage requires a high involvement of humans. Developers are prone to making assumptions about what the user needs and expects; therefore, it is important to maintain regular interactions with the stakeholders. But methods to manually collect data from the users, like interviews and surveys, are tedious and take a lot of time and effort. They are also subject to a sampling bias; interviewing only a small portion of the target user base leads to a biased representation of viewpoints. \cite{Use_of_personas_in_Requirements_Engineering}
According to the paper "Use Cases for Design Personas: A Systematic Review and New Frontiers," 40\% of all software development projects use personas \cite{Use_Cases_for_Design_Personas}. One obvious advantage of personas is the convenience; using personas and demographics is definitely faster and easier than interviewing the stakeholders. They offer the developer a diverse understanding of the stakeholder and are critical to the development and design of the UI/UX \cite{Who_uses_personas_in_requirements_engineering}. 
The demographic gives the developers an insight into the characteristics of their target audience. It contains important data such as age, gender, location, education, income, and more \cite{Why_and_How_to_Use_Demographics_in_UX}. 
With this data, general assumptions can be made, but it lacks the specific needs and expectations of the end-users.
Personas can be a vital tool for requirement engineering in the requirement elicitation and validation stage \cite{Who_uses_personas_in_requirements_engineering}. Personas contain the end-users' key requirements as preferences and needs. With this additional information and context, developers can more clearly specify the requirements \cite{Use_of_personas_in_Requirements_Engineering, Who_uses_personas_in_requirements_engineering}. Using mental modeling, developers can comprehend how the persona would interact with the project and make requirements accordingly \cite{Use_Cases_for_Design_Personas}. 
In the validation step, personas can help developers identify issues such as overlapping requirements and redundant requirements \cite{Use_of_personas_in_Requirements_Engineering}.